---
title: "Run random breeding schemes"
output: github_document
params:
  nRepetition: 3
  simSetupFile: 'simSetup/simSetup_8257d5b9f5db15da5156443270fa82b9.rds'
  seed: 1993
  proposedPoints: 4
  nCpuBO: 4
  totalIter: 4
  BOdirectory: 'realEffectsBO/boResults'
  outFolder: 'realEffectsBO'
---

```{r setup, include=FALSE}
knitStartTime <- Sys.time()
knitr::opts_chunk$set(echo = TRUE,
                      # format
                      tidy = FALSE, # format code with 'tidy_source()'
                      tidy.opts = list(width.cutoff = 80),
                      strip.white = TRUE #remove the white lines in the beginning or end of a source chunk
)
```

# Run simple BO breeding schemes

The breeder draw randomly the markers effects and use BO to 
optimise the breeding scheme and use the optimised parameter for the entire 
campaign.

### Load libraries

Loading the library and source the file containing a R function of the project.

```{r packages}
suppressPackageStartupMessages({
  library(gaston)
  library(TSP)
  library(breedSimulatR)
  library(digest)
  library(glmnet)
  library(mlrMBO)
  library(parallelMap)
  library(parallel)
  library(lhs)
  library(dotenv)
})
```

### Return compilation parameters:

```{r}
print(params)
outFolder <- params$outFolder
if (!dir.exists(outFolder)) {
  dir.create(outFolder, recursive = TRUE)
}
if (!dir.exists(params$BOdirectory)) {
  dir.create(params$BOdirectory, recursive = TRUE)
}
```



## Simulate simple BO breeding schemes


```{r}
totalCPU <- detectCores()
nCPU <- floor(totalCPU / params$nCpuBO)
simSetup <- readRDS(params$simSetupFile)
```


```{r}
source('src/simulation.R')
source('src/utils.R')
```


## Optimisation setup

"Optimization setups" contains all the information about the optimization parameters (eg. number of iterations, number of points evaluated parallely at each iterations, aquisition function (for bayesian otpimization) ... ). This helps to run the same on different breeding constraints.

Only one optimization setup will be used.

```{r optSetup}
optP <- list(
  kernel = 'gauss', # kernel of the gaussian process
  final.method = 'best.predicted', # see mlrmbo documentation (`??makeMBOControl`) and below
  acquFunction = makeMBOInfillCritEI(),
  filter.proposed.points = TRUE, # should bayesian opt avoid sampling parameters too close to each-other
  filter.proposed.points.tol = 0.001, # threshold defining if 2 points are too close to each-other
  propose.points = params$proposedPoints, # number of points evaluated at each iteration
  nCpusProposePoints = params$nCpuBO, # number of core to use for evaluating the points at each iteration
  totalIter = params$totalIter, # total number of iteration
  # time.budget = 60*30, # total time available for the optimization
  initTrainSize = 5, # initial training data size
  funEval = 1, # see below
  nCpusFunEval = 1 # see below
)
```




```{r}
# # example of one simulation:
# simSetup$fixedParams$genoChipSNP <- simSetup$fixedParams$trait$qtn
# simTime <- Sys.time()
# x <- breedSimOpt(
#   i = 0.1,
#   iHomo = 0.3,
#   bRep = 0.4,
#   phenoFreq = 1,
#   seed = 1993,
#   budget = simSetup$fixedParams$budget,
#   nGen = simSetup$fixedParams$nGen,
#   initPop = simSetup$fixedParams$initPop,
#   plotCost = simSetup$fixedParams$plotCost,
#   newIndCost = simSetup$fixedParams$newIndCost,
#   trait = simSetup$fixedParams$trait,
#   phenotyper = simSetup$fixedParams$phenotyper,
#   # genoChipSNP = simSetup$fixedParams$genoChipSNP,
#   genoChipSNP = simSetup$fixedParams$trait$qtn,
#   createModel = simSetup$fixedParams$createModel,
#   selectMateInds = simSetup$fixedParams$selectMateInds,
#   aggrFun = simSetup$fixedParams$aggrFun,
#   aggrFunName = simSetup$fixedParams$aggrFunName,
#   verbose = TRUE
# )
# simTime <- Sys.time() - simTime
# print(simTime)
```







# create list of random seeds for the optimisation

```{r}
set.seed(params$seed)
# draw list of seeds to be able to reproduce the results
seeds <- as.integer(sample.int(.Machine$integer.max, params$nRepetition))
```




# run simulations


```{r}
source('src/setupSimulation.R')
source('src/optimization.R')
sim_env <- new.env(parent = globalenv())
source('src/simulation.R', local = sim_env)
```


```{r}

res <- mcmapply(function(x){
  
  simStartTime <- Sys.time()
  set.seed(x[1])
  
  # remove use all qtn for genotyping
  simSetup$fixedParams$genoChipSNP <- simSetup$fixedParams$trait$qtn
  
  # run BO
  BOseed <- sample.int(1000000, 1)
  BOresults <- bayesianOptimization(
    mainSeed = BOseed,
    simSetup = simSetup,
    optP = optP,
    outputFolder = params$BOdirectory)
  
  
  
  # breeding campaign with the optimized parameters.
  simSeed <- sample.int(1000000, 1)
  simRes <- breedSimOpt(
    i = BOresults$bestPoint$i,
    iHomo = BOresults$bestPoint$iHomo,
    bRep = BOresults$bestPoint$bRep,
    phenoFreq = BOresults$bestPoint$phenoFreq,
    seed = simSeed,
    budget = simSetup$fixedParams$budget,
    nGen = simSetup$fixedParams$nGen,
    initPop = simSetup$fixedParams$initPop,
    plotCost = simSetup$fixedParams$plotCost,
    newIndCost = simSetup$fixedParams$newIndCost,
    trait = simSetup$fixedParams$trait,
    phenotyper = simSetup$fixedParams$phenotyper,
    genoChipSNP = simSetup$fixedParams$genoChipSNP,
    createModel = simSetup$fixedParams$createModel,
    selectMateInds = simSetup$fixedParams$selectMateInds,
    aggrFun = simSetup$fixedParams$aggrFun,
    aggrFunName = simSetup$fixedParams$aggrFunName,
    verbose = FALSE
  )
  
  
  res <- data.frame(
    i = BOresults$bestPoint$i,
    iHomo = BOresults$bestPoint$iHomo,
    bRep = BOresults$bestPoint$bRep,
    phenoFreq = BOresults$bestPoint$phenoFreq,
    mainSeed = x[1], # main seed of the calculation
    BOseed = BOseed, # seed used for the BO
    simSeed = simSeed, # seed used for the breeding simulation
    BV = simRes)
  colnames(res)[8] <- paste0("BV_", simSetup$fixedParams$aggrFunName)
  
  res$simulationTime <- as.numeric(Sys.time() - simStartTime, units = 'secs')
  res$method <- 'BO-realEffects'
  res$simSetupFile <- params$simSetupFile
  res$nGen <- simSetup$fixedParams$nGen
  res$he <- simSetup$setupInfo$he
  res$plotBudjetPerGen <- simSetup$fixedParams$plotBudjetPerGen
  

  resultFile <- file.path(outFolder,
                          paste0("realEffectsBOScheme",
                                 digest(res),
                                 "-", x[1]))
  resF <-  paste0(resultFile, '.csv')
  i <- 1
  while (file.exists(resF)) {
    i <- i + 1
    resF <- paste0(resultFile, '_', i, '.csv')
  }
  write.csv(res, file = resF, row.names = FALSE)
  
  res
},
x = seeds,
SIMPLIFY = FALSE,
mc.cores = nCPU,
mc.preschedule = FALSE)

```


```{r}
res <- do.call(rbind, res)

resultFile <- file.path(outFolder,
                        paste0("aggregated-realEffectsBOScheme_", digest(res)))
resF <-  paste0(resultFile, '.csv')

i <- 1
while (file.exists(resF)) {
  i <- i + 1
  resF <- paste0(resultFile, '_', i, '.csv')
}

write.csv(res, file = resF, row.names = FALSE)

```



# Appendix {-}

There is some information about the R session used to run the optimizations:

```{r sessionInfo, echo=FALSE}
  options(max.print = 10000)
  cat("Document generated in:\n")
  print(Sys.time() - knitStartTime)
  if (Sys.info()["sysname"] == "Linux") {
    cat("\nCPU: ")
    cat(unique(system("awk -F': ' '/model name/{print $2}' /proc/cpuinfo", intern = T)))
    cat("\nMemory total size: ")
    cat(as.numeric(system("awk '/MemTotal/ {print $2}' /proc/meminfo", intern = T))*10^(-6), "GB")
  }
  cat("\n\n\nSession information:\n")
  print(sessionInfo(), locale = FALSE)
```
