---
title: "Run random breeding schemes"
output: github_document
params:
  nRepetition: 3
  simSetupFile: 'simSetup/simSetup_8257d5b9f5db15da5156443270fa82b9.rds'
  seed: 1993
  outFolder: NULL
---

```{r setup, include=FALSE}
knitStartTime <- Sys.time()
knitr::opts_chunk$set(echo = TRUE,
                      # format
                      tidy = FALSE, # format code with 'tidy_source()'
                      tidy.opts = list(width.cutoff = 80),
                      strip.white = TRUE #remove the white lines in the beginning or end of a source chunk
)
```

# Run random breeding schemes


### Load libraries

Loading the library and source the file containing a R function of the project.

```{r packages}
suppressPackageStartupMessages({
  library(gaston)
  library(TSP)
  library(breedSimulatR)
  library(digest)
  library(glmnet)
  library(mlrMBO)
  library(parallelMap)
  library(parallel)
  library(lhs)
  library(dotenv)
})
```

### Return compilation parameters:

```{r}
print(params)
outFolder = ifelse(is.null(params$outFolder), "randomSchemes", params$outFolder)
if (!dir.exists(outFolder)) {
  dir.create(outFolder, recursive = TRUE)
}
```



## Simulate random breeding schemes

Here we simulate some breeding scheme with random parameters.

We use the "real" phenotyper (which use the "real" markers effects) to phenotype the individuals.


```{r}
nCPU <- detectCores()
simSetup <- readRDS(params$simSetupFile)
```


```{r}
source('src/simulation.R')
```

```{r}
set.seed(params$seed)

sampledParams <- sapply(simSetup$optParams$pars, function(param) {
  if (param$type == "numeric") {
    round(runif(params$nRepetition , param$lower, param$upper), digits = 4)
  } else if (param$type == "integer") {
    sample(param$lower:param$upper, params$nRepetition, replace = TRUE)
  }
})
# draw list of seeds to be able to reproduce the results
seed <- as.integer(sample.int(.Machine$integer.max, params$nRepetition))
sampledParams <- cbind(sampledParams, seed)
```



```{r}
# # example of one simulation:
# x <- breedSimOpt(
#   i = 0.1,
#   iHomo = 0.3,
#   bRep = 0.4,
#   phenoFreq = 1,
#   seed = 1993,
#   budget = simSetup$fixedParams$budget,
#   nGen = simSetup$fixedParams$nGen,
#   initPop = simSetup$fixedParams$initPop,
#   plotCost = simSetup$fixedParams$plotCost,
#   newIndCost = simSetup$fixedParams$newIndCost,
#   trait = simSetup$fixedParams$trait,
#   phenotyper = simSetup$fixedParams$phenotyper,
#   genoChipSNP = simSetup$fixedParams$genoChipSNP,
#   createModel = simSetup$fixedParams$createModel,
#   selectMateInds = simSetup$fixedParams$selectMateInds,
#   aggrFun = simSetup$fixedParams$aggrFun,
#   aggrFunName = simSetup$fixedParams$aggrFunName,
#   verbose = TRUE
# )
```


```{r}
parallelStartMulticore(cpus = nCPU,
                       show.info = TRUE,
                       load.balancing = TRUE)
parallelRegisterLevels(levels = "objective")
missingSchemes <- sampledParams
res <- NULL
while (nrow(missingSchemes) != 0) {
  resList <- parallelMap(function(x){
    simStartTime <- Sys.time()
    simRes <- breedSimOpt(
      i = x[1],
      iHomo = x[2],
      bRep = x[3],
      phenoFreq = x[4],
      seed = x[5],
      budget = simSetup$fixedParams$budget,
      nGen = simSetup$fixedParams$nGen,
      initPop = simSetup$fixedParams$initPop,
      plotCost = simSetup$fixedParams$plotCost,
      newIndCost = simSetup$fixedParams$newIndCost,
      trait = simSetup$fixedParams$trait,
      phenotyper = simSetup$fixedParams$phenotyper,
      genoChipSNP = simSetup$fixedParams$genoChipSNP,
      createModel = simSetup$fixedParams$createModel,
      selectMateInds = simSetup$fixedParams$selectMateInds,
      aggrFun = simSetup$fixedParams$aggrFun,
      aggrFunName = simSetup$fixedParams$aggrFunName,
      verbose = FALSE
    )
    
    res <- data.frame(
      i = x[1],
      iHomo = x[2],
      bRep = x[3],
      phenoFreq = x[4],
      seed = x[5],
      BV = rnorm(1) )#simRes)
    colnames(res)[6] <- paste0("BV_", simSetup$fixedParams$aggrFunName)
    
    res$simulationTime <- as.numeric(Sys.time() - simStartTime, units = 'secs')
    res$method <- 'random'
    res$simSetupFile <- params$simSetupFile
    res$nGen <- simSetup$fixedParams$nGen
    res$he <- simSetup$setupInfo$he
    res$plotBudjetPerGen <- simSetup$fixedParams$plotBudjetPerGen
    
    
    
    resultFile <- file.path(outFolder,
                            paste0("randomScheme_", digest(res)))
    resF <-  paste0(resultFile, '.csv')
    i <- 1
    while (file.exists(resF)) {
      i <- i + 1
      resF <- paste0(resultFile, '_', i, '.csv')
    }
    write.csv(res, file = resF, row.names = FALSE)
    res
  },
  split(missingSchemes, seq(nrow(missingSchemes))),
  simplify = FALSE,
  level = "custom.objective")
  
  if (is.null(res)) {
    res <- do.call(rbind, resList)
  } else {
    res <- rbind(res, do.call(rbind, resList))
  }
  
  mergedDF <- rbind(res[, colnames(sampledParams)], sampledParams)
  dup <- duplicated(mergedDF)[(nrow(res)+1):(nrow(res)+nrow(sampledParams))]
  newMissingSchemes <- sampledParams[which(!dup),]
  
  if (isTRUE(all.equal(newMissingSchemes, missingSchemes))) {
    warning("Fail to calculate some schemes:")
    print(missingSchemes)
    break
  } else {
    missingSchemes <- newMissingSchemes
  }

}
parallelStop()
```


```{r}
resultFile <- file.path(outFolder,
                        paste0("aggregated-randomScheme_", digest(res)))
resF <-  paste0(resultFile, '.csv')

i <- 1
while (file.exists(resF)) {
  i <- i + 1
  resF <- paste0(resultFile, '_', i, '.csv')
}

write.csv(res, file = resF, row.names = FALSE)
```



# Appendix {-}

There is some information about the R session used to run the optimizations:

```{r sessionInfo, echo=FALSE}
  options(max.print = 10000)
  cat("Document generated in:\n")
  print(Sys.time() - knitStartTime)
  if (Sys.info()["sysname"] == "Linux") {
    cat("\nCPU: ")
    cat(unique(system("awk -F': ' '/model name/{print $2}' /proc/cpuinfo", intern = T)))
    cat("\nMemory total size: ")
    cat(as.numeric(system("awk '/MemTotal/ {print $2}' /proc/meminfo", intern = T))*10^(-6), "GB")
  }
  cat("\n\n\nSession information:\n")
  print(sessionInfo(), locale = FALSE)
```
